Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
fin order
tidy, reflow

## Caribou socioecology
Caribou are gregarious
ungulates with fission-fusion dynamics [@Lesmerises_2018] that display temporal
and spatial variation in social networks [@Peignier_2019]. In winter, caribou
dig holes in the snow, termed craters, to access forage [@Bergerud_1974].
Cratering is presumed to be a costly behaviour and as a result, caribou tend to
occupy and re-use craters once they are established. <!-- and there is
considerably less access to forage than when the landscape is snow-free.-->
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
cover and, in winter, variable distribution of craters on the landscape.

@@

### Network layer construction
<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and land cover). Two season
elementary-layers (summer and winter) and three land cover elementary-layers
(foraging, forest, and open) combined for a total of six layers. Single layers were
composed of individuals linked by social associations, for each season and land cover combination.-->

We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
individuals were associating if simultaneous GPS fixes were within the spatial
distance threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes and associations between
individuals in a given network layer were represented as intralayer
edges.

@@

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, forest and
open) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.
<!-- JWT: Your graphs present things in the order of Foraging, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->

>>>>

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
In winter, caribou dig holes in the snow, termed craters, to access forage
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
cover and, in winter, variable distribution of craters on the landscape.

@@

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
individuals were associating if simultaneous GPS fixes were within the spatial
distance threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes and associations between
individuals in a given network layer were represented as intralayer
edges.

@@

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, forest and
open) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.
